Time series clusters

### 2021-09-22 src/old/ts_clusters.Rmd
tidy up

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)
library(imputeTS)
library(tsbox)
library(dtwclust)
library(leaflet)
library(ggmap)

@@

ggplot(la.f, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  theme_nothing(legend = TRUE) +
  labs(title = "Upload clusters") +
  scale_fill_viridis_d()+
  theme_void()

@@

>>>>

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)
library(imputeTS)
library(tsbox)
library(dtwclust)
library(leaflet)
library(ggmap)
library(cowplot)

@@

@@

cluster.upL <- c(6, 9, 11, 12, 13)
cluster.upS <- c(1, 2, 3, 7, 8, 10)

la.f_ <- la.f #plot the background

cluster.upL.plot <- la.f %>% 
  filter(cluster.up %in% cluster.upL) %>% 
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(data = la.f_, color='grey', fill='white', aes(x=long, y=lat, group=group, colour = 'grey30')) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  labs(title = "Larger clusters, upload speeds") + 
  scale_fill_viridis_d() +
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()

cluster.upS.plot <- la.f %>% 
  filter(cluster.up %in% cluster.upS) %>% 
  ggplot(aes(x = long, y = lat)) +
  geom_polygon(data = la.f_, color='grey', fill='white', aes(x=long, y=lat, group=group, colour = 'grey30')) +
  geom_polygon(aes( group = group, fill = as.factor(cluster.up))) +
  labs(title = "Smaller clusters, upload speeds") + 
  scale_fill_viridis_d() +
  guides(fill=guide_legend(title="Clusters")) +
  theme_void()

plot_grid(cluster.upL.plot, cluster.upS.plot, nrow = 1,
          align = "h", axis = "l", 
          #labels = c(".co.uk / pop., 2000", ".co.uk / pop., 2010", "non .co.uk / pop., 2000", "non .co.uk / pop., 2010", ""), 
          #label_size = 12,
          greedy = T)
          #rel_heights = c(1, 1, .3)) # this is the relative position of the 3 lines

#ggsave("all_maps2.png") # this is the colour map for the preprint
out.path.map <- paste0(path, "/paper/v1/figures/map.up.clusters.png")
ggsave(out.path.map)#,
       #width = 210, #A4
       #height = 297, #A4
       #units = "mm")
```

### 2021-09-22 src/old/ts_clusters_k11.Rmd
tidy up

---
title: "Time series clusters, k = 5"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

# Define k instead of selecting it
k <- 5

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_all_5.csv", sep = "")
write_csv(clusters, out.clusters)

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_nodiff_5.csv", sep = "")
write_csv(clusters.nodiff, out.clusters)

@@

#ggsave("all_maps2.png") # this is the colour map for the preprint
# out.path.map <- paste0(path, "/paper/v1/figures/map.up.clusters5.png")
# ggsave(out.path.map)#,
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```

>>>>

---
title: "Time series clusters, k = 11"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

# Define k instead of selecting it
k <- 11

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_all_11.csv", sep = "")
write_csv(clusters, out.clusters)

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_nodiff_11.csv", sep = "")
write_csv(clusters.nodiff, out.clusters)

@@

#ggsave("all_maps2.png") # this is the colour map for the preprint
# out.path.map <- paste0(path, "/paper/v1/figures/map.up.clusters11.png")
# ggsave(out.path.map)#,
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```

### 2021-09-22 src/old/ts_clusters_k7.Rmd
tidy up

---
title: "Time series clusters, k = 11"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

# Define k instead of selecting it
k <- 11

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_all_11.csv", sep = "")
write_csv(clusters, out.clusters)

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_nodiff_11.csv", sep = "")
write_csv(clusters.nodiff, out.clusters)

@@

#ggsave("all_maps2.png") # this is the colour map for the preprint
# out.path.map <- paste0(path, "/paper/v1/figures/map.up.clusters11.png")
# ggsave(out.path.map)#,
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```

>>>>

---
title: "Time series clusters, k = 7"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

@@

# Define k instead of selecting it
k <- 7

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_all_7.csv", sep = "")
write_csv(clusters, out.clusters)

@@

# save clusters file
out.clusters <- paste(path, "/data/temp/clusters_nodiff_7.csv", sep = "")
write_csv(clusters.nodiff, out.clusters)

@@

#ggsave("all_maps2.png") # this is the colour map for the preprint
# out.path.map <- paste0(path, "/paper/v1/figures/map.up.clusters7.png")
# ggsave(out.path.map)#,
#width = 210, #A4
#height = 297, #A4
#units = "mm")
```

### 2021-09-22 src/old/ts_clusters_old.Rmd
tidy up

---
title: "Time series plots"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)

@@

# map LA mean test frequency per date
la@data <- left_join(la@data, la.dateAvg, by = "LAD19NM")
var <- la@data[ ,'mean(n)']
breaks <- classIntervals(var, n = 5, style = "quantile")
my_colours <- brewer.pal(5, "Blues")
plot(la, col = my_colours[findInterval(var, breaks$brks, all.inside = TRUE)], axes = FALSE,
                 border = rgb(0.8, 0.8, 0.8, 0))
# drop LA
rm(la)
```

## Keep working hours

@@

## Download speeds

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.down <- bb2020sp %>%
  group_by(date,LAD19NM) %>%
  summarise(mean.down = mean(speeddown))#, mean.down = mean(speeddown), n.tests = n())
sapply(ts.down, function(x) sum(is.na(x)))

# https://www.data-to-viz.com/caveat/spaghetti.html

mean.down.uk <- ts.down %>%
  group_by(date) %>%
  summarise(mean.down.uk = mean(mean.down))#, mean.down = mean(speeddown), n.tests = n())

start.date =  "2019-12-31"

ggplot(subset(ts.down,date > start.date), aes(x=as.POSIXct(date), y=mean.down, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Download speeds") + #xlab("") +
  ylab("download speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.down.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.down.uk, group = 1), colour="green") #

@@

## Upload speeds

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.up <- bb2020sp %>%
  group_by(date,LAD19NM) %>%
  summarise(mean.up = mean(speedup))
sapply(ts.up, function(x) sum(is.na(x)))

# https://www.data-to-viz.com/caveat/spaghetti.html

mean.up.uk <- ts.up %>%
  group_by(date) %>%
  summarise(mean.up.uk = mean(mean.up))

start.date =  "2019-12-31"

ggplot(subset(ts.up,date > start.date), aes(x=as.POSIXct(date), y=mean.up, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Upload speeds") + #xlab("") +
  ylab("upload speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.up.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.up.uk, group = 1), colour="green") #

## Speed tests

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.tests <- bb2020sp %>%
  group_by(date,LAD19NM) %>%
  summarise(n.tests = n())
sapply(ts.tests, function(x) sum(is.na(x)))

# https://www.data-to-viz.com/caveat/spaghetti.html

# n.tests.uk <- ts.tests %>%
#   group_by(date.block) %>%
#   summarise(n.tests = n()/382)

mean.tests.uk <- ts.tests %>%
  group_by(date) %>%
  summarise(mean.tests.uk = mean(n.tests))

start.date =  "2019-12-31"

ggplot(subset(ts.tests,date > start.date), aes(x=as.POSIXct(date), y=n.tests, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("N. of tests") + #xlab("") +
  ylab("tests") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2, scales = "free_y") +
  geom_line(data = subset(mean.tests.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.tests.uk, group = 1), colour="green") #.uk

## Download diff 2020 - 2019

ts.down.diff <- ts.down
ts.down.diff$date.lag1y <- ts.down.diff$date - years(1)
ts.down.diff <- merge(ts.down.diff,ts.down.diff, by.x = c("date.lag1y", "LAD19NM"), by.y = c("date","LAD19NM"), all = F)

ts.down.diff <- ts.down.diff %>%
  rename(mean.down2019 = mean.down.y, mean.down2020 = mean.down.x) %>%
  select(-date.lag1y.y)

ts.down.diff$diff <- ts.down.diff$mean.down2020 - ts.down.diff$mean.down2019

head(ts.down.diff)
sapply(ts.down.diff, function(x) sum(is.na(x)))

# https://www.data-to-viz.com/caveat/spaghetti.html

mean.down.diff.uk <- ts.down.diff %>%
  group_by(date) %>%
  summarise(mean.down.diff.uk = mean(diff))#, mean.down = mean(speeddown), n.tests = n())

start.date =  "2019-12-31"

ggplot(subset(ts.down.diff,date > start.date), aes(x=as.POSIXct(date), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in download speeds") + #xlab("") +
  ylab("diff. in download speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.down.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.down.uk, group = 1), colour="green") #
```

## Upload diff 2020 - 2019

ts.up.diff <- ts.up
ts.up.diff$date.lag1y <- ts.up.diff$date - years(1)
ts.up.diff <- merge(ts.up.diff,ts.up.diff, by.x = c("date.lag1y", "LAD19NM"), by.y = c("date","LAD19NM"), all = F)

ts.up.diff <- ts.up.diff %>%
  rename(mean.up2019 = mean.up.y, mean.up2020 = mean.up.x) %>%
  select(-date.lag1y.y)

ts.up.diff$diff <- ts.up.diff$mean.up2020 - ts.up.diff$mean.up2019

head(ts.up.diff)
sapply(ts.up.diff, function(x) sum(is.na(x)))

# https://www.data-to-viz.com/caveat/spaghetti.html

mean.up.diff.uk <- ts.up.diff %>%
  group_by(date) %>%
  summarise(mean.up.diff.uk = mean(diff))#, mean.up = mean(speedup), n.tests = n())

start.date =  "2019-12-31"

ggplot(subset(ts.up.diff,date > start.date), aes(x=as.POSIXct(date), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in upload speeds") + #xlab("") +
  ylab("diff. in upload speed") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.up.diff.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.up.diff.uk, group = 1), colour="green") #
```

## Speed tests diff. 2020 - 2019

```{r include=TRUE, echo=FALSE, results= 'markup', message=FALSE, warning = FALSE, fig.height=600, fig.width=14}
ts.tests.diff <- ts.tests
ts.tests.diff$date.lag1y <- ts.tests.diff$date - years(1)
ts.tests.diff <- merge(ts.tests.diff,ts.tests.diff, by.x = c("date.lag1y", "LAD19NM"), by.y = c("date","LAD19NM"), all = F)

ts.tests.diff <- ts.tests.diff %>%
  rename(n.tests2019 = n.tests.y, n.tests2020 = n.tests.x) %>%
  select(-date.lag1y.y)

ts.tests.diff$diff <- ts.tests.diff$n.tests2020 - ts.tests.diff$n.tests2019

head(ts.tests.diff)
sapply(ts.tests.diff, function(x) sum(is.na(x)))

mean.tests.diff.uk <- ts.tests.diff %>%
  group_by(date) %>%
  summarise(mean.tests.diff.uk = mean(diff))

start.date =  "2019-12-31"

ggplot(subset(ts.tests.diff,date > start.date), aes(x=as.POSIXct(date), y=diff, group = LAD19NM, colour = "red")) +
  geom_line() + guides(colour=FALSE) + ggtitle("Diff. in speed tests") + #xlab("") +
  ylab("diff. in speed tests") +
  scale_y_continuous(labels = scales::comma) +
  scale_x_datetime(date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~LAD19NM, ncol = 2) +
  geom_line(data = subset(mean.tests.diff.uk,date > start.date), aes(x=as.POSIXct(date), y=mean.tests.diff.uk, group = 1), colour="green") #
```

>>>>

---
title: "Time series clusters"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output")
  })
---

```{r settings, include = FALSE}
library(tsbox)
library(ggplot2)
library(tidyverse)
library(geojsonio)
library(tsfeatures)
library(rprojroot)
library(openair)
library(reshape2)
library(lubridate)
library(rgdal)
library(maptools)
library(sp)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(knitr)
library(rprojroot)
library(viridis)
library(hrbrthemes)
library(imputeTS)
library(tsbox)
library(dtwclust)

@@

# map LA mean test frequency per date
la@data <- left_join(la@data, la.dateAvg, by = "LAD19NM")
var <- la@data[ ,'mean(n)']
breaks <- classIntervals(var, n = 5, style = "quantile")
my_colours <- brewer.pal(5, "Blues")
plot(la, col = my_colours[findInterval(var, breaks$brks, all.inside = TRUE)], axes = FALSE,
                 border = rgb(0.8, 0.8, 0.8, 0))

## Keep working hours and days

The time series are based on mean upload and download speeds as well as the total number of tests for working days and during working hours

@@

## Time series clusters

I create clusters based on upload, download and number of tests time series for tests working hours and days from 16/2/2020 onwards.

More work needs to be done to select the optimal *k* as well as the clustering methods.
The `dtwclust` package comes with quite some readings, saved in the `.\literature\`.

Also, we need to think about upload / download / differnces / period + **imputation**.

# download
ts.down <- TS2020 %>%
  group_by(weekday, hour, LAD19NM) %>%
  summarise(mean.down = mean(speeddown))#, mean.down = mean(speeddown), n.tests = n())

# upload
ts.up <- TS2020 %>%
  group_by(weekday, hour, LAD19NM) %>%
  summarise(mean.up = mean(speedup))

# tests
ts.tests <- TS2020 %>%
  group_by(weekday, hour, LAD19NM) %>%
  summarise(n.tests = n())
```

### Upload speed

```{r eval=TRUE, echo=TRUE, results= 'markup', message=FALSE, warning = FALSE, fig.height=10, fig.width=10}

# upload working hours and days

ts.wide <- ts.up %>%
  select(date, LAD19NM, mean.up) %>%
  filter(date > "2020-2-15")

# turn to a wide format
ts.wide <- ts_wide(ts.wide)

# impute with means
library(imputeTS)
ts.wide <- na_mean(ts.wide)
#sapply(ts.wide, function(x) sum(is.na(x)))

# extract names
ts.wide.names <- names(ts.wide[,-1])
ts.wide <- ts.wide[,-1]

# standardise
ts.wide <- zscore(ts.wide)

# convert to list for tsclust
ts.wide <- split(ts.wide, rep(1:ncol(ts.wide), each = nrow(ts.wide)))

# 5 - 20 cluster sollutions
pc_k <- tsclust(ts.wide, k = c(5,10,15,20), seed = 94L,
                type="partitional",
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))

# decide k, see RJ-2019-023 for max/min
names(pc_k) <- paste0("k_", c("5","10","15", "20"))
sapply(pc_k, cvi, type = "internal")

# I need to work on the selection

pc_k <- tsclust(ts.wide, k = 20, seed = 94L, 
                type="partitional", 
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))

plot(pc_k)

cluster_up <- data.frame(LAD=ts.wide.names,
                           cluster=pc_k@cluster)
```

### Download speed

```{r eval=TRUE, echo=TRUE, results= 'markup', message=FALSE, warning = FALSE, fig.height=10, fig.width=10}

# download working hours and days

ts.wide <- ts.down %>%
  select(date, LAD19NM, mean.down) %>%
  filter(date > "2020-2-15")

# turn to a wide format
ts.wide <- ts_wide(ts.wide)

# impute with means
library(imputeTS)
ts.wide <- na_mean(ts.wide)
#sapply(ts.wide, function(x) sum(is.na(x)))

# extract names
ts.wide.names <- names(ts.wide[,-1])
ts.wide <- ts.wide[,-1]

# standardise
ts.wide <- zscore(ts.wide)

# convert to list for tsclust
ts.wide <- split(ts.wide, rep(1:ncol(ts.wide), each = nrow(ts.wide)))

# 5 - 20 cluster sollutions
pc_k <- tsclust(ts.wide, k = c(5,10,15,20), seed = 94L,
                type="partitional",
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))

# decide k, see RJ-2019-023 for max/min
names(pc_k) <- paste0("k_", c("5","10","15", "20"))
sapply(pc_k, cvi, type = "internal")

# I need to work on the selection

pc_k <- tsclust(ts.wide, k = 20, seed = 94L, 
                type="partitional", 
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))

plot(pc_k)

cluster_down <- data.frame(LAD=ts.wide.names,
                         cluster=pc_k@cluster)
```

### N. of speeds

```{r eval=TRUE, echo=TRUE, results= 'markup', message=FALSE, warning = FALSE, fig.height=10, fig.width=10}

# tests working hours and days

ts.wide <- ts.tests %>%
  select(date, LAD19NM, n.tests) %>%
  filter(date > "2020-2-15")

# turn to a wide format
ts.wide <- ts_wide(ts.wide)

# impute with means
library(imputeTS)
ts.wide <- na_mean(ts.wide)
#sapply(ts.wide, function(x) sum(is.na(x)))

# extract names
ts.wide.names <- names(ts.wide[,-1])
ts.wide <- ts.wide[,-1]

# standardise
ts.wide <- zscore(ts.wide)

# convert to list for tsclust
ts.wide <- split(ts.wide, rep(1:ncol(ts.wide), each = nrow(ts.wide)))

# 5 - 20 cluster sollutions
pc_k <- tsclust(ts.wide, k = c(5,10,15,20), seed = 94L,
                type="partitional",
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))

# decide k, see RJ-2019-023 for max/min
names(pc_k) <- paste0("k_", c("5","10","15", "20"))
sapply(pc_k, cvi, type = "internal")

# I need to work on the selection

pc_k <- tsclust(ts.wide, k = 15, seed = 94L, 
                type="partitional", 
                distance = "dtw_basic", centroid = "pam", trace = T, 
                args = tsclust_args(dist = list(window.size = 20L)))

plot(pc_k)

cluster_tests <- data.frame(LAD=ts.wide.names,
                           cluster=pc_k@cluster)

clusters <- merge(cluster_up, cluster_down, by = "LAD")
names(clusters)[2] <- "cluster.up"
names(clusters)[3] <- "cluster.down"
clusters <- merge(clusters, cluster_tests, by = "LAD")
names(clusters)[4] <- "cluster.tests"
#sapply(clusters, function(x) sum(is.na(x)))

clusters  %>% arrange(cluster.up) %>% kable() 
```

## Mapping the clusters

la@data <- merge(la@data, clusters, by.x = "LAD19NM", by.y = "LAD")

var <- la@data[ ,'cluster.up']
plot(la, col = var, main = "Upload clusters",
     border = rgb(0.8, 0.8, 0.8, 0))

var <- la@data[ ,'cluster.down']
plot(la, col = var, main = "Download clusters",
     border = rgb(0.8, 0.8, 0.8, 0))

var <- la@data[ ,'cluster.tests']
plot(la, col = var, main = "Tests clusters",
     border = rgb(0.8, 0.8, 0.8, 0))

@@
